\large Neural, Tree, and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-06-25 docs/papers/sto/so.tex
FIXUP draft methods: add SR subsection

\vspace{1em}
\subsection{SO function}

We use the \texttt{PySR} \citep{Cranmer2023} symbolic regression code to
fit for an analytic function expression of the SO neural network.

@@

\vspace{1em}
\subsection{Simulation and Differentiation}

@@

Our observable $\vo$ is a snapshot $\hat\vz = (\hat\vx, \hat\vp)^\intercal$ at a
given time $a_o$, which in general can be given by the interpolation of two
snapshots $\vz_{k-1}$ and $\vz_k$ where $a_{k-1} \leq a_o < a_k$.
Then ${\p\vo}/{\p\vz_i}$ would be zero except for the relevant $\vz_{k-1}$ and
$\vz_k$.
We have in the initial conditions of the adjoint equations
\begin{align}
  \vxi_n &= \frac{\p\cJ}{\p\vo} \cdot \frac{\p\vo}{\p\vx_n}, \nonumber\\
  \vpi_n &= \frac{\p\cJ}{\p\vo} \cdot \frac{\p\vo}{\p\vp_n}.
\end{align}
In the reverse time evolution of the adjoint equations, these adjoint varibales
remain zero until the time stepping from $a_{k+1}$ to $a_k$.

@@

\vspace{1em}
\subsection{Optimization of Dynamics}
\label{sec:so}

@@

\vspace{1em}
\subsection{Simulations}

@@

\vspace{1em}
\subsection{Training}

@@

>>>>

@@

\vspace{1em}
\subsection{Differentiable Simulation}

@@

We refer to the quantities that are directly related to the objective function
as the observables. Our observable $\vo$ is a snapshot $\hat\vz = (\hat\vx,
\hat\vp)^\intercal$ at a given time $a_o$, which in general can be given by the
interpolation of two snapshots $\vz_{k-1}$ and $\vz_k$ where $a_{k-1} \leq a_o <
a_k$. Then ${\p\vo}/{\p\vz_i}$ would be zero except for the relevant $\vz_{k-1}$
and $\vz_k$. We have in the initial conditions of the adjoint equations
\begin{align}
  \vxi_n &= \frac{\p\cJ}{\p\vo} \cdot \frac{\p\vo}{\p\vx_n}, \nonumber\\
  \vpi_n &= \frac{\p\cJ}{\p\vo} \cdot \frac{\p\vo}{\p\vp_n}.
\end{align}
In the reverse time evolution of the adjoint equations, these adjoint varibales
remain zero until the time stepping from $a_{k+1}$ to $a_k$.

\vspace{1em}
\subsection{Spatial Optimization of Dynamics}
\label{sec:so}

@@

@@

\vspace{1em}
\subsection{Target Data for Training and Testing}

@@

\vspace{1em}
\subsection{Training of SO neural networks}

@@

\vspace{1em}
\subsection{Symbolic Regression}

We use the \texttt{PySR} \citep{Cranmer2023} symbolic regression code to fit for
analytic function expressions of the trained SO neural networks.
